Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-06-01 EMNLP-demo-paper/system.tex
typo

However, when the text sequence becomes signification longer, i.e., a full paragraph in the machine comprehension task,  even the simplified sentence cannot be meaningfully represented in the graph or matrix visual encoding. To address this visualization challenge, as illustrated in Figure~\ref{fig:attentionVis}(d), we introduce a hierarchical representation. Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated attention information for the whole paragraph. The user can focus on localized attention information by selecting a pixel bar that presents a single sentence (the colored blocks in the bar correspond to individual works). We also link this attention representation with matrix form, such that whenever a sentence is selected the local attention is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).

>>>>

However, when the text sequence becomes significantly longer, i.e., a full paragraph in the machine comprehension task,  even the simplified sentence cannot be meaningfully represented in the graph or matrix visual encoding. To address this visualization challenge, as illustrated in Figure~\ref{fig:attentionVis}(d), we introduce a hierarchical representation. Here, a pure graphical encoding (the color bars marked by \emph{att2}) is used to capture the aggregated attention information for the whole paragraph. The user can focus on localized attention information by selecting a pixel bar that presents a single sentence (the colored blocks in the bar correspond to individual works). We also link this attention representation with matrix form, such that whenever a sentence is selected the local attention is shown in the matrix view (see Figure~\ref{fig:MCexample}(a)).
